\SW: II. Did we beat the lens finding robots in CFHTLS?

### 2014-09-13 doc/sw-cfhtls.tex

The CFHT Legacy Survey has been searched for strong lenses with
semi-automated algorithms both at galaxy and groups scales. With the aim
of improving these lens finding robots, we carry out a blind lens search
in the complete \cfhtls WIDE survey with \sw. We describe the training
sample used for both training the citizen scientists that participated
in \sw and calibrating their performance. We generate realistic looking
simulated samples of lenses both at galaxy and group-scales as part of
this training sample. We present 74 new strong gravitational lens
candidates discovered from the \sw-\cfhtls search. Furthermore, we
compile a sample of false positives which can be used for robot testing,
first of its kind for the lensing community. The simulated sample is
also used to make a comparison between human performance against the
robots. We find that the XX per cent of the known lens sample is
recovered and the new lens sample has XX completeness with respect to
the simulated sample. We make available the following data products:
simulated sample, simulation code and the false positives sample at XXX.

@@

We selected a sample of 450 duds for the Stage I classification in \sw
(see XXX) and a sample of XXX false positives for the Stage II
inspection (see XXX). The sample of false positives was selected from
the candidates which passed the Stage I of \sw. We note that this is the
first time, we have a systematically compiled sample of visually
inspected false positives by the \sw users and categorized by the
science team. Such a sample is tremendously helpful for training and
understanding performances of various lens finding algorithms (refer
james, sherry's paper ? XXX)
{\bf TBA data products; make the FP sample available}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%
%\begin{longtable*}{l c c c c c c c l}
%\caption{ \label{tab:all} 
%Characteristics of lens candidates from the \SA sample. }\\
%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
%\endfirsthead
%
%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
%\endhead
%
%\hline  
%\multicolumn{11}{p{15cm}}{
%{\bfseries
%{\bf m:} This galaxy falls within the masked region as per the catalog from
%which the magnitudes and the redshift are extracted.  {\bf z:} The magnitudes
%and/or redshift are not from the catalog instead are measured by the author.
%}  }\\
%
%\endlastfoot
%   SW1  & 02:01:21.89 & $-$09:15:15.09 & 19.90 &  0.46 &  2.2 &   2.0 & A &  SA18 \\ 
%   SW2  & 02:02:10.50 & $-$11:09:11.68 & 17.80 &  0.48 &  5.0 &   3.7 & A &  SA87 \\ 
%\end{longtable*}
%

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0.pdf}
\caption{ \label{fig:lch1}
Sample of promising lens candidates ($R_{avg}>=2.0$)
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0_1.pdf}
\caption{ \label{fig:lch2}
contd. - Sample of promising lens candidates ($R_{avg}>=2.0$)
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_1p3_1p7.pdf}
\caption{ \label{fig:lcl}
Sample of low probability lens candidates ($1.0<R_{avg}<2.0$)
}
\end{center}
\end{figure*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{Recovery of known \cfhtls lenses from \sw}
\label{sec:results:reco}

>>>>

The CFHT Legacy Survey has been searched for strong lenses with
semi-automated algorithms both at galaxy and groups scales. With the aim
of improving these lens finding robots, we carry out a blind lens search
in the complete \cfhtls WIDE survey with \sw. We describe the training
sample used for both training the citizen scientists that participated
in \sw and calibrating their performance. We generate realistic looking
simulated samples of lenses both at galaxy and group-scales as part of
this training sample. We present 80 new strong gravitational lens
candidates discovered from the \sw-\cfhtls search out of which 40
candidates are promising. Furthermore, we compile a sample of false
positives which can be used for robot testing, first of its kind for the
lensing community. The simulated sample is also used to make a
comparison between human performance against the robots. We find that
the XX per cent of the known lens sample is recovered and the new lens
sample has XX completeness with respect to the simulated sample. We make
available the following data products: simulated sample, simulation code
and the false positives sample at XXX.

@@

We selected a sample of 450 duds for the Stage I classification in \sw
(see XXX) and a sample of XXX false positives for the Stage II
inspection (see XXX). The sample of false positives was selected from
the candidates which passed the Stage I of \sw. We note that this is the
first time, we have a systematically compiled sample of visually
inspected false positives by the \sw users and categorized by the
science team. Such a sample is tremendously helpful for training and
understanding performances of various lens finding algorithms (refer
james, sherry's paper ? XXX)
{\bf TBA data products; make the FP sample available}

@@

\onecolumn

\begin{center}
\begin{longtable}{lcccccccccr}
\caption{ \label{tab:swcands} 
Thresholds used in the selection of the simulated lenses. }\\
\hline
SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & R$_{avg}$ & ZooID & P & Comments  \\
  &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\ 
\hline
\endfirsthead
\hline
SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & R$_{avg}$ & ZooID & P & Comments  \\
  &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\ 
\hline
\endhead
\hline
\multicolumn{11}{p{18cm}}{
The column Comments has two type of notes. The first is about the lens
image configuration where the symbols mean the following A: Arc, D: Double, Q:
Quad, R: Ring. The second is a comment on the type of lens assessed
visually. Note that this classification is not based on colors or spectral
analysis. The symbols are E: Elliptical, S: (face on) Spiral, G: Group-scale, D:
Edge on disk, R: Red starforming galaxy.  This galaxy falls within the masked region as per the catalog from
which the magnitudes and the redshift are extracted.  
}\\  
\endlastfoot
 SW1 & CFHTLS J020338-051901 &   30.9097 &   -5.3171 &  0.4 & 18.8 &  1.6 &  2.0 & ASW0001sqw &  0.7  &  D,E   \\ 
 SW2 & CFHTLS J020341-074722 &   30.9223 &   -7.7897 &  0.5 & 18.8 &  1.6 &  2.0 & ASW000993q &  1.0  &  A,E   \\ 
 SW3 & CFHTLS J020457-110309 &   31.2392 &  -11.0526 &  0.7 & 20.0 &  1.6 &  2.3 & ASW00099b9 &  1.0  &  A,R   \\ 
 SW4 & CFHTLS J020642-095157 &   31.6751 &   -9.8659 &  --  &  --  &  0.9 &  2.0 & ASW0001ld7 &  1.0  &  A,R   \\ 
 SW5 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  --  &  --  &  1.8 &  1.3 & ASW0001c3j &  1.0  &  A,R   \\ 
 SW6 & CFHTLS J020832-043315 &   32.1339 &   -4.5544 &  --  &  --  &  1.6 &  2.3 & ASW0002asp &  1.0  &  A,R   \\ 
 SW7 & CFHTLS J020848-042427 &   32.2011 &   -4.4076 &  --  &  --  &  1.1 &  2.7 & ASW0002bmc &  1.0  &  D,D   \\ 
 SW8 & CFHTLS J020849-050429 &   32.2078 &   -5.0748 &  --  &  --  &  0.9 &  2.3 & ASW0002qtn &  1.0  &  A,R   \\ 
 SW9 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.5  &  D,S   \\ 
SW10 & CFHTLS J021057-084450 &   32.7415 &   -8.7474 &  --  &  --  &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\ 
SW11 & CFHTLS J021221-105251 &   33.0881 &  -10.8811 &  0.3 & 17.9 &  1.8 &  2.0 & ASW0002dx7 &  1.0  &  D,E/S   \\ 
SW12 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.7 & ASW00024id &  1.0  &  R,R   \\ 
SW13 & CFHTLS J021230-074727 &   33.1264 &   -7.7909 &  0.9 & 20.3 &  1.7 &  1.7 & ASW0001ze0 &  0.5  &  A,R/G   \\ 
SW14 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.6  &  A,R/E   \\ 
SW15 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.3 & ASW00021r0 &  0.5  &  A,R/G   \\ 
SW16 & CFHTLS J022016-102446 &   35.0688 &  -10.4129 &  0.6 & 19.4 &  1.5 &  2.3 & ASW0009a4w &  0.7  &  D,E   \\ 
SW17 & CFHTLS J022359-083651 &   35.9995 &   -8.6144 &  --  &  --  &  3.1 &  1.3 & ASW0004iye &  0.7  &  A,E   \\ 
SW18 & CFHTLS J022406-062846 &   36.0256 &   -6.4796 &  0.4 & 19.6 &  0.9 &  2.3 & ASW0003wsu &  1.0  &  A,E   \\ 
SW19 & CFHTLS J022409-105808 &   36.0398 &  -10.9689 &  --  &  --  &  4.8 &  3.0 & ASW0004dv8 &  1.0  &  A,G   \\ 
SW20 & CFHTLS J022533-053204 &   36.3888 &   -5.5346 &  0.5 & 19.4 &  3.6 &  2.0 & ASW0004m3x &  0.7  &  A,R/G   \\ 
SW21 & CFHTLS J022716-105602 &   36.8186 &  -10.9341 &  0.4 & 17.3 &  1.8 &  2.0 & ASW0009ab8 &  0.8  &  A,E/G   \\ 
SW22 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.7  &  A,R   \\ 
SW23 & CFHTLS J022805-051733 &   37.0236 &   -5.2927 &  0.4 & 18.8 &  1.4 &  2.3 & ASW0009ans &  1.0  &  Q,E   \\ 
SW24 & CFHTLS J022817-080242 &   37.0727 &   -8.0452 &  0.5 & 19.6 &  0.9 &  2.0 & ASW00042d9 &  1.0  &  A,E/R   \\ 
SW25 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.4  &  D/A,E   \\ 
SW26 & CFHTLS J023008-054038 &   37.5359 &   -5.6774 &  0.6 & 19.7 &  1.9 &  2.3 & ASW0003r61 &  0.6  &  A,E   \\ 
SW27 & CFHTLS J023010-110409 &   37.5420 &  -11.0694 &  0.9 & 20.6 &  1.2 &  1.7 & ASW0004fgb &  0.7  &  A,R   \\ 
SW28 & CFHTLS J023051-082423 &   37.7141 &   -8.4064 &  --  &  --  &  0.8 &  2.3 & ASW000412m &  0.6  &  A,E   \\ 
SW29 & CFHTLS J023123-082535 &   37.8468 &   -8.4266 &  --  &  --  &  1.2 &  2.3 & ASW0004xjk &  0.4  &  A,R   \\ 
SW30 & CFHTLS J023315-042243 &   38.3133 &   -4.3789 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  1.0  &  A,R   \\ 
SW31 & CFHTLS J023325-053104 &   38.3547 &   -5.5178 &  0.5 & 18.8 &  1.3 &  1.7 & ASW0005ire &  1.0  &  Q,M   \\ 
SW32 & CFHTLS J023453-093032 &   38.7232 &   -9.5089 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.5  &  A,D   \\ 
SW33 & CFHTLS J084833-044051 &  132.1385 &   -4.6809 &  0.7 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.9  &  A,R   \\ 
SW34 & CFHTLS J084841-045237 &  132.1708 &   -4.8772 &  0.3 & 19.0 &  1.0 &  2.3 & ASW0004nan &  1.0  &  A,E   \\ 
SW35 & CFHTLS J084941-051650 &  132.4216 &   -5.2808 &  0.4 & 19.1 &  1.5 &  1.3 & ASW0004nh3 &  0.6  &  A,E/S   \\ 
SW36 & CFHTLS J085135-052232 &  132.8980 &   -5.3756 &  --  &  --  &  1.9 &  1.3 & ASW0004n2x &  0.7  &  D,R   \\ 
SW37 & CFHTLS J085317-020312 &  133.3233 &   -2.0535 &  0.7 & 20.6 &  1.2 &  1.3 & ASW0000vtc &  0.7  &  A,R   \\ 
SW38 & CFHTLS J090218-053924 &  135.5790 &   -5.6567 &  --  &  --  &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\ 
SW39 & CFHTLS J090248-010232 &  135.7020 &   -1.0424 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.8  &  D,E   \\ 
SW40 & CFHTLS J090308-043252 &  135.7840 &   -4.5479 &  --  &  --  &  1.2 &  2.0 & ASW00007mq &  0.8  &  A,E   \\ 
SW41 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  --  & 19.8 &  1.2 &  1.7 & ASW00007ls &  0.6  &  A,R/E   \\ 
SW42 & CFHTLS J090333-005829 &  135.8890 &   -0.9749 &  --  &  --  &  2.1 &  1.7 & ASW00008a0 &  1.0  &  A/D,E/G   \\ 
SW43 & CFHTLS J135724+561614 &  209.3540 &   56.2707 &  --  &  --  &  2.6 &  1.3 & ASW0006e0o &  1.0  &  D,E   \\ 
SW44 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  1.0  &  D,D   \\ 
SW45 & CFHTLS J140027+541028 &  210.1160 &   54.1745 &  --  &  --  &  1.2 &  1.3 & ASW0006a07 &  0.8  &  Q,R/E   \\ 
SW46 & CFHTLS J140030+574437 &  210.1260 &   57.7437 &  0.4 & 18.2 &  2.0 &  2.3 & ASW0009bp2 &  0.9  &  A,E   \\ 
SW47 & CFHTLS J140425+520506 &  211.1062 &   52.0850 &  0.4 & 18.9 &  1.4 &  1.3 & ASW0005o0w &  0.9  &  D,E   \\ 
SW48 & CFHTLS J140522+574333 &  211.3426 &   57.7259 &  0.7 & 19.7 &  1.0 &  2.7 & ASW000619d &  1.0  &  A,R   \\ 
SW49 & CFHTLS J140622+520942 &  211.5958 &   52.1617 &  0.7 & 20.3 &  1.2 &  2.3 & ASW0005rnb &  1.0  &  A,R   \\ 
SW50 & CFHTLS J140845+514913 &  212.1907 &   51.8205 &  0.7 & 19.7 &  1.5 &  2.7 & ASW0005o38 &  1.0  &  A,E   \\ 
SW51 & CFHTLS J141056+533225 &  212.7364 &   53.5405 &  0.6 & 19.4 &  1.7 &  2.0 & ASW0006kjx &  0.6  &  A,R/G   \\ 
SW52 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  1.0  &  A,R   \\ 
SW53 & CFHTLS J141448+545548 &  213.7010 &   54.9301 &  0.4 & 18.3 &  2.1 &  1.3 & ASW0006zc9 &  0.4  &  A,G   \\ 
SW54 & CFHTLS J141518+513915 &  213.8290 &   51.6542 &  0.4 & 18.3 &  3.0 &  1.7 & ASW00070vl &  1.0  &  D,E   \\ 
SW55 & CFHTLS J141927+533919 &  214.8627 &   53.6554 &  0.7 & 20.5 &  2.3 &  1.7 & ASW0006yrw &  0.5  &  A,R/G   \\ 
SW56 & CFHTLS J142432+550019 &  216.1354 &   55.0055 &  0.5 & 19.5 &  1.1 &  2.0 & ASW0007vx2 &  1.0  &  A,E   \\ 
SW57 & CFHTLS J142603+511421 &  216.5140 &   51.2393 &  --  &  --  &  4.4 &  2.7 & ASW0006mea &  1.0  &  A,G   \\ 
SW58 & CFHTLS J142620+561356 &  216.5870 &   56.2323 &  0.4 & 19.5 &  1.3 &  1.3 & ASW0007sez &  1.0  &  A/R,S   \\ 
SW59 & CFHTLS J142652+560001 &  216.7200 &   56.0004 &  --  &  --  &  1.5 &  1.7 & ASW0007t5y &  1.0  &  R,R   \\ 
SW60 & CFHTLS J142843+543713 &  217.1815 &   54.6204 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.9  &  D,D   \\ 
SW61 & CFHTLS J142934+562541 &  217.3926 &   56.4281 &  0.5 & 19.0 &  5.9 &  2.7 & ASW0009cjs &  1.0  &  A,G   \\ 
SW62 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  1.0  &  A,R   \\ 
SW63 & CFHTLS J143100+564603 &  217.7510 &   56.7675 &  --  &  --  &  1.8 &  1.7 & ASW00086xq &  1.0  &  A,E   \\ 
SW64 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  2.0 & ASW0009cox &  0.9  &  A,R/G   \\ 
SW65 & CFHTLS J143454+522850 &  218.7270 &   52.4808 &  0.6 & 19.4 &  4.4 &  2.3 & ASW0007k4r &  0.4  &  Q,G/R   \\ 
SW66 & CFHTLS J143627+563832 &  219.1164 &   56.6425 &  0.5 & 19.5 &  1.5 &  2.3 & ASW0008swn &  1.0  &  A,D   \\ 
SW67 & CFHTLS J143631+571131 &  219.1315 &   57.1922 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.8  &  D/A,R   \\ 
SW68 & CFHTLS J143651+530705 &  219.2150 &   53.1183 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007h27 &  1.0  &  A,E/G   \\ 
SW69 & CFHTLS J143658+533807 &  219.2425 &   53.6355 &  0.7 & 19.6 &  0.9 &  2.7 & ASW0007hu2 &  0.9  &  D,D   \\ 
SW70 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  1.0  &  A,R   \\ 
SW71 & CFHTLS J143950+544606 &  219.9610 &   54.7686 &  --  &  --  &  1.7 &  1.3 & ASW00085cp &  0.6  &  A,G/R   \\ 
SW72 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\ 
SW73 & CFHTLS J220256+023432 &  330.7370 &    2.5758 &  --  &  --  &  6.8 &  2.3 & ASW0007e08 &  1.0  &  A,G/C   \\ 
SW74 & CFHTLS J220722+013610 &  331.8441 &    1.6030 &  0.8 & 20.3 &  1.0 &  2.0 & ASW0001uuz &  0.6  &  A,R   \\ 
SW75 & CFHTLS J221101+003401 &  332.7582 &    0.5671 &  0.9 & 20.0 &  1.1 &  1.3 & ASW00090l5 &  1.0  &  A,E/R   \\ 
SW76 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  --  & 17.1 &  1.4 &  1.7 & ASW0008wmr &  1.0  &  A,S   \\ 
SW77 & CFHTLS J221513+010240 &  333.8060 &    1.0445 &  --  &  --  &  0.8 &  1.7 & ASW0008dxh &  0.6  &  A,R/G   \\ 
SW78 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  1.0  &  A,D   \\ 
SW79 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R   \\ 
SW80 & CFHTLS J222007-002505 &  335.0307 &   -0.4182 &  0.3 & 21.4 &  1.2 &  2.0 & ASW00094fq &  1.0  &  Q,R/G   \\ 
\end{longtable}
\end{center}

\twocolumn

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0.pdf}
\caption{ \label{fig:lch1}
Sample of high probability lens candidates ($R_{avg}>=2.0$).
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_1p3_1p7.pdf}
\caption{ \label{fig:lcl}
Sample of medium probability lens candidates ($1.0<R_{avg}<2.0$).
}
\end{center}
\end{figure*}

\subsection{Recovery of known \cfhtls lenses from \sw}
\label{sec:results:reco}
